---
title: "Introduction to Quarto (2 of 2)"
author: "Dr. F.J. Rodenburg"
format: pdf
editor: visual
---

This file renders to PDF, using \LaTeX. This has two big advantages over Word:

-   A more professional look

-   Vector graphics (you can zoom in forever, while retaining image quality)

## Using packages

Debugging a large report can be a pain. One simple improvement is including all necessary packages at the top. This way, any missing packages can be easily identified:

```{r}
library("sfsmisc") # contains eaxis() function for nice axes
```

*(When you type a hashtag (`#`), what follows is not interpreted as code, but as a comment.)*

**Exercise**:

-   Try rendering this Quarto file. If you see a bar at the top that says *"Package (...) required but it is not installed,"* click *"Install"* and wait for the download and installation to finish. Then, click **Render**.
    -   If you're using **Windows** or **linux**, a shortcut for rendering is CTRL+Shift+K.
    -   If you're using **OSX** (Mac), a shortcut for rendering is Cmd+Shift+K.

\clearpage

## Cross-referencing figures

In part one we saw how to include a figure, change its height and width in the rendered Word file, and how to include a caption. Now let's try and cross-reference it in the text.

**Exercise**:

-   Following the example on the Quarto website [here](https://quarto.org/docs/authoring/cross-references.html#computations), add a label to the figure below and edit the sentence underneath the code chunk to cross-reference the figure. *(Replace the dots (...) with the cross-reference.)*

```{r}
#| echo: false
#| fig.width: 5
#| fig.height: 3
#| dpi: 300
#| fig.cap: "Example of box plots using a standard data set in R."

par(mar = c(4, 4, 1, 1) + 0.1)
plot(Sepal.Length ~ Species, data = iris, axes = FALSE, 
     ylab = "Sepal length (mm)", 
     boxwex = 0.25, staplewex = 0, col = "steelblue", 
     lty = 1, lwd = 2, pch = 16)
axis(1, 1:3, levels(iris$Species), tick = FALSE)
eaxis(2)
par(mar = c(5, 4, 4, 3) + 0.1)
```

In ... we see an example of R's plotting capabilities.

## Old-school R markdown

If you have prior experience with R markdown, I have good news: Quarto uses nearly identical syntax!

**Exercise**:

-   To see the the R markdown code that underlies this Quarto file, go to the upper-left corner where you see *"Source"* and *"Visual."* Click on **Source**.

-   You can switch back and forth any time between the two views.

## Including citations to scientific literature

Professional documents would not be complete without the support for citations to scientific literature.

**Exercise**:

-   Search any peer-reviewed scientific article of your liking and note the DOI (document object identifier)

-   Place your cursor at the end of the sentence below, go to **Insert** at the top of the source pane and choose *"Citation..."* Choose *"From DOI"* and enter the DOI you just looked up.

-   Render the document to confirm you have a working citation.

Look mom, my first Quarto citation:

-   Prefer old-school R markdown? See this video: <https://youtu.be/zuuOYjE8m98>

## References
