---
title: "Introduction to Quarto (1 of 2)"
author: "Dr. F.J. Rodenburg"
format: docx
editor: visual
---

## How to use this file

Quarto allows you to weave together code, output and commentary into a single document. This means there is no need to clumsily copy-paste output into Word: We can simply generate a Word file by clicking the **Render** button at the top.

**Exercise**:

-   Look for the **Render** button at the top of the source pane and click it.

-   If you don't know what is meant by "source pane," have a look at the video explaining the RStudio interface: <https://youtu.be/AHAR7j-IUOw>

-   Nothing happens, run into errors, or otherwise unable to render the file?

    -   Where did you save this file? Check whether a Word document was just created in this location. If so, everything worked correctly!

    -   Ask the course coordinators for help. That's what we're here for!

## Including code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
3 + 7
```

You can [add options](https://quarto.org/docs/computations/execution-options.html) to executable code like this:

```{r}
#| echo: false
3 + 7
```

**Exercise**:

-   Render the file again and scroll down to the section "**Including code**" what is the difference between the first and second example? What did `echo: false` accomplish?

## Creating a new code block

In an empty line, if you type a forward slash (/), you can see some examples of what you can insert in a Quarto file.

**Exercise**:

-   Place your cursor in the empty space below this line and type a forward slash (/). Choose *"R code chunk"*. Add a simple arithmetic operation to the R chunk (e.g. `2 + 2 * 4` and click **Render** to confirm the code is working.

## 

-   Don't see any empty space? Move your cursor to the end of this line and press Enter twice.

## Including plots

Here is a quick example of a basic figure that includes a caption. To avoid clutter, we again suppress the code used with the option `echo: false`.

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 5
#| dpi: 300

plot(Sepal.Length ~ Species, data = iris)
```

**Exercise**:

-   This figure is missing a caption. Add a chunk option to include a caption that says: "Example of box plots using a standard data set in R."

-   Not sure how to do so? Check out the [options](https://quarto.org/docs/computations/execution-options.html#caption-and-alt-text) on the Quarto website.

-   To test whether it worked, try rendering your file again and inspect the Word file.

Once you are finished, you may close this file and proceed with part 2.

## 
